Distributional Trees and Forests

### 2017-06-23 pkg/disttree/inst/useR2017/slides.Rnw
use transparency rather than line type for scale
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1484 255f4249-2263-4417-b1ea-8498779e27a7

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<1->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt='n', yaxt='n', ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 5, main = "")
@
}
\end{center}
\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt='n', yaxt='n', ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 5, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<3->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt='n', yaxt='n', ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd=5)
lines(x = x, y = ytrue+0.1+var, col = pal["forest"], lty = 1, lwd = 2)
lines(x = x, y = ytrue-0.1-var, col = pal["forest"], lty = 1, lwd = 2)
@
}
\end{center}
\endminipage

>>>>

\begin{frame}[fragile]
\frametitle{Motivation}
\vspace{-0.41cm}
\begin{figure}[!htb]
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GLM, echo=FALSE, results=hide>>=
nobs <- 200
## GLM
set.seed(7)
x <- c(1:nobs)/nobs
ytrue <- 1+x*1.5
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<1->{
<<plot_motivation_GLM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt='n', yaxt='n', ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 5, main = "")
@
}
\end{center}
\endminipage
\visible<2->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAM, echo=FALSE, results=hide>>=
## GAM
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3 
y <- ytrue + rnorm(nobs,0,0.3)
@
\visible<2->{
<<plot_motivation_GAM, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(y=y , x=x, xaxt='n', yaxt='n', ann=FALSE, col = "slategray", pch = 19)
box(lwd=5)
lines(x = x, y = ytrue, col = pal["forest"], lwd = 5, main = "")
@
}
\end{center}
\endminipage
\visible<3->{{\LARGE$\rightarrow$}}
\minipage{0.29\textwidth}
\begin{center}
<<motivation_GAMLSS, echo=FALSE, results=hide>>=
## GAMLSS
set.seed(7)
x <- c(1:nobs)/nobs
x <- 2*(x-0.5)
ytrue <- x^3
var <- exp(-(2*x)^2)/2
y <- ytrue + rnorm(nobs, 0, 0.1 + var)
@
\visible<3->{
<<plot_motivation_GAMLSS, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = hcl(10, 100, 50, alpha = 0.2), border = "transparent")
lines(x, ytrue, col = pal["forest"], lwd=5)
points(x, y, col = "slategray", pch = 19)
box(lwd = 5)
@
}
\end{center}
\endminipage
